An OpenCL Implementation of Wait-Free Sets

### 2015-06-12 Docs/paper.tex
doc updated

%\documentclass[9pt,twocolumn]{IEEEtran}
%\documentclass[12pt,twoside,draft]{IEEEtran}
%\documentclass[12pt,draft]{IEEEtran}
%\documentclass[11pt,draft]{IEEEtran}
%\documentclass[11pt,final]{IEEEtran}
%\documentclass[11pt,ds,final]{my_IEEEtran}
\documentclass[11pt,onecolumn,draftcls]{IEEEtran}
%\documentclass[11pt]{IEEEtran}
%\documentclass[11pt]{IEEEtran}
%\documentclass[draft]{IEEEtran}
%\documentclass[9pt,twocolumn,technote,twoside]{IEEEtran}

@@

\section{Proof of Correctness}
{\fontsize{20}{20}
\begin{algorithm}
  \caption{Algorithm to delete marked nodes}
  \label{alg:deleteMarkedNode}
  \begin{algorithmic}[1]
    \Function{delMarkedNodes}{startRef, nextRef\&, nodePool}
      \State doneFlag = false;
      \While{(!doneFlag)}    
        \State [nextRef,startMark] := getPtr(startRef);
        \If{(!startMark)}
          \State [nextNextRef,nextMark] := getPtr(nextRef);
          \If{(nextMark)}
            \State casFlag = CAS(startRef:next,[nextRef,startMark],[nextNextRef,startMark]);
            \If{casFlag}
               \State PUT(nodePool,nextRef);
            \EndIf
          \Else
            \State
            \Return true;
          \EndIf
        \Else{}
          \State
          \Return false;  
        \EndIf
      \EndWhile        
    \EndFunction
  \end{algorithmic}
\end{algorithm}
}

@@

\begin{algorithm}
  \caption{Algorithm to find a key}
  \label{alg:find}
  \begin{algorithmic}[1]
    \Function{find}{key, nodePool}
       \State lid := getSIMDIndex();
       \State startRef := hashFunction(key);
       \State doneFlag := false;
       \While{(!doneFlag)}
          \State prevRef := startRef;
          \If{(lid = 1)}
             \State delStatus = delMarkedNode(prevRef,nextRef\&,nodePool);
          \EndIf
          \State waitAllSIMD();
          \State delStatus = broadcastSIMD(delStatus,1);
          \If{delStatus = true}
             \State maxVal = maxSIMD(nodePool,nextRef);
             \If{maxVal < key}
                \State prevRef = nextRef;
             \Else
                \State doneFlag = true;
                \If(anySIMD(val[lid] = key))
                   \Return true;
                \Else
                   \Return false;   
                \EndIf   
             \EndIf
          \Else
             \State prevRef = startRef;   
          \EndIf
       \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}

>>>>

%\documentclass[9pt,twocolumn]{IEEEtran}
%\documentclass[12pt,twoside,draft]{IEEEtran}
%\documentclass[12pt,draft]{IEEEtran}
%\documentclass[11pt,draft]{IEEEtran}
%\documentclass[11pt,final]{IEEEtran}
%\documentclass[11pt,ds,final]{my_IEEEtran}
%\documentclass[11pt,onecolumn,draftcls]{IEEEtran}
%\documentclass[11pt]{IEEEtran}
\documentclass[11pt,onecolumn]{IEEEtran}
%\documentclass[draft]{IEEEtran}
%\documentclass[9pt,twocolumn,technote,twoside]{IEEEtran}

@@

\section{Proof of Correctness}
\begin{algorithm}
  \caption{Delete all marked nodes}
  \label{alg:deleteMarkedNode}
  \begin{algorithmic}[5]
    \Function{delMarkedNodes}{startRef, nodePool}
      \State doneFlag = false;
      \While{(!doneFlag)}    
        \State [nextRef,startMark] := getPtr(startRef);
        \If{(!startMark)}
          \State [nextNextRef,nextMark] := getPtr(nextRef);
          \If{(nextMark)}
            \State casFlag = CAS(startRef:next,[nextRef,startMark],[nextNextRef,startMark]);
            \If{casFlag}
               \State freeNode(nodePool,nextRef);
            \EndIf
          \Else
            \State
            \Return true;
          \EndIf
        \Else{}
          \State
          \Return false;  
        \EndIf
      \EndWhile        
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
  \caption{Check next node for key}
  \label{alg:check}
  \begin{algorithmic}[5]
    \Function{checkKey}{key, prevRef\&, nodePool}
       \State [nextRef,prevMark] := getPtr(prevRef);
       \If {(prevMark)}
         \State
         \Return {\small NODE\_DELETED}.
       \EndIf
       \If {(nextRef = 0)}
         \State
         \Return {\small KEY\_NOT\_DELETED}.
       \EndIf

       \State [nnRef,nextMark] := getPtr(nextRef);
       \If {(nextMark)}
         \State
         \Return {\small NODE\_NEXT}.
       \EndIf

       \State maxVal := simdMax(nodePool,nextRef);
         \If{maxVal $<$ key}
            \State prevRef := nextRef;
            \Return {\small NODE\_NEXT}.
         \Else
           \If{simdAny(val[lid] = key)}
               \State
               \Return {\small KEY\_FOUND};
           \Else
               \State               
               \Return {\small KEY\_NOT\_FOUND};   
           \EndIf   
         \EndIf
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Find a key in the set}
  \label{alg:find}
  \begin{algorithmic}[5]
    \Function{find}{key, prevRef\&, nodePool}
       \State lid := simdGetIndex();
       \State startRef := hashFunction(key);
       \State prevRef  := startRef;
       \State doneFlag := false;
       \While{(!doneFlag)}
          \If{(lid = 1)}
             \State delStatus := delMarkedNode(prevRef,nodePool);
          \EndIf
          \State simdBarrier();
          \State delStatus = simdBroadcast(delStatus,1);
          \If{delStatus = true}
             \State keyStatus := checkKey(key, prevRef, nodePool);
             \If{(keyStatus = NODE\_DELETED)}
                \State prevRef := startRef;
             \ElsIf{(keyStatus = KEY\_FOUND)}
                \State 
                \Return true
             \ElsIf{(keyStatus = KEY\_NOT\_FOUND)}
                \State 
                \Return false
             \EndIf
          \Else
             \State prevRef := startRef;   
          \EndIf
       \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Insert a key in the set}
  \label{alg:insert}
  \begin{algorithmic}[5]  
    \Function{insert}{key, nodePool}
      \State doneFlag := false;
      \While{(!doneFlag)}
        \State findStatus := find(key, prevRef\&, nextRef\&, nodePool);
        \If{(findStaus = true)}
          \State
          \Return false;
        \EndIf
        \State minIndex := getMinEmptySlot(nextRef,nodePool);
        \If{minIndex = 0} \Comment No empty slot.
          \State insertStatus := insertNodeAndKey(key, prevRef\&,nextRef\&,nodePool);
        \Else
          \State insertStatus := insertKey(key, minIndex, nextRef\&,nodePool);
        \EndIf
        \If{insertStatus = true}
          \State
          \Return true;
        \EndIf
      \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Find empty slot with minimum index}
  \label{alg:minindex}
  \begin{algorithmic}[5]  
    \Function{getMinEmptySlot}{nextRef, nodePool}
      \State val := nodePool[nextRef]:V[lid];
      \State indicator := (val = EMPTY\_SLOT)?lid:0;
      \If {(simdALL(indicator = 0))}
        \State minIndex := 0;
      \Else
        \State minIndex := simdMin(indicator);
      \EndIf
      \Return minIndex;        
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Insert a node and a key}
  \label{alg:insnodekey}
  \begin{algorithmic}[5]  
    \Function{insertNodeAndKey}{key, prevRef\&, nextRef\&, nodePool}
      \State newNRef := Alloc(nodePool);
      \State newNNRef := Alloc(nodePool);
      \State newNRef:next := [newNNRef,0];
      \If{(nodePool[nextRef]:V[lid] < key)}
        \State nodePool[newNRef]:V[lid] := nodePool[nextRef]:V[lid];
        \State nodePool[newNNRef]:V[lid] := EMPTY\_SLOT;
      \Else
        \State nodePool[newNNRef]:V[lid] := nodePool[nextRef]:V[lid];
        \State nodePool[newNPRef]:V[lid] := EMPTY\_SLOT;
      \EndIf
      \State minIndex := getMinEmptySlot(newNRef,nodePool);
      \State nodePool[newNRef]:V[minIndex] := key;
      \State nodePool[newNNPtr]:next := [nextRef,0];
      \State status := CAS(nodePool[prevRef]:next,[nextRef,0],newNPtr);
      \Return status;
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Insert a key in a node}
  \label{alg:inskey}
  \begin{algorithmic}[5]  
    \Function{insertKey}{key, minIndex, nextRef\&, nodePool}
      \If{lid = 1}
        \State status := CAS(nodePool[nextRef]:V[minIndex],EMPTY\_SLOT,key);
      \EndIf
      \State simdWait();
      \State status = simdBroadcast(status, 1);
      \Return status;
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Delete a key from the set}
  \label{alg:delkey}
  \begin{algorithmic}[5]  
    \Function{remove}{key, nodePool}
      \State doneFlag := false;
      \While{(!doneFlag)}
        \State findStatus := find(key, prevRef\&, nextRef\&, nodePool);
        \If{(findStaus = false)}
          \State
          \Return false;
        \EndIf
        \State val   := nodePool[nextRef]:V[lid];
        \If{(val = key)}
          \State status := CAS(nodePool[nextRef]:V[lid],key,EMPTY\_SLOT);
        \EndIf
        \State simdWait();
        \State status := simdBrodacast(status);
        \If{(status = true)}
          \State status := deleteNode(prevRef\&, nextRef\&, nodePool);
          \Return status;
        \Else
          \State
          \Return false;
        \EndIf
      \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Delete a node}
  \label{alg:delnode}
  \begin{algorithmic}[5]  
    \Function{deleteNode}{prevRef\&, nextRef\&, nodePool}
         \State val := nodePool[nextRef]:V[lid];
         \State status := simdAll(val,EMPTY\_SLOT);
         \If{(status = true)}
           \State [nnRef,nextMark] := getPtr(nextRef);
           \State newMark := 1;
           \If{(lid = 1)}
              \State status := CAS(nodePool[nextRef]:next,[nnRef,nextMark],[nnRef,newMark]);
              \If{(status = true)}
                \State status = delMarkedNodes(prevRef,NodePool); 
              \EndIf
           \EndIf
           \State simdWait();
           \State status = simdBroadcast(status,1);
           \State
           \Return status;
         \EndIf
    \EndFunction
  \end{algorithmic}
\end{algorithm}
